\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Physics 242 Final Assignment\\Invidual Report}
\author{Lingyi Kong}
\date{June 10, 2016}

\begin{document}

\maketitle

I was mostly in charge of understanding the theory behind our project and help my teammates translating them into the code.
Initially, I proposed the project of doing double slit problem, but it was rejected because it had inherent incompatibility with Markov Chain Monte Carlo simulation. Later my teammate Xiaojian Jin proposed our current project which applied MCMC to the financial model and simulate stock price and predict option price. Because I had zero background in finance, I was very sure what we need to do at the beginning. Therefore, I didn't contribute much at initial stage, while Xiaojian was building the toy model and Juan was preparing the code structure for the project. As we moved along the project, we faced some difficulties because we couldn't find many examples to learn. At that time, it was inevitable that we should have a much better understanding of the theory. Since I was more familiar with the Markov Chain Monte Carlo simulation from assignment 3, I took the charge of understanding the whole theory about the stochastic equation in Black Schole's equation and geometric Brownian motion, which help my team to finalize our code. I also prepared the slides and did most of the presentation part.
We did suffer from things falling behind schedules due to technical difficulties and starting late. But overall, our team contributed equally to the project and we got some fine result in the end.

\end{document}
